\bf The \texttt{forestecology} R package for modeling interspecies competition between trees

### 2021-02-19 etc/paper/forestecology.Rmd
impletemented ideas from Mensh 2017

A high-level overview of the steps of our analysis pipeline is as follows:

1. Compute the growth of trees based on census data
1. Add spatial information:
    1. Define buffer region trees.
    1. Add spatial cross-validation block information.
1. Identify all focal and corresponding competitor trees.
1. Fit model, make predictions, and visualize model results

Additionally,

@@

```{r scbi-trees, out.width="66%", fig.cap="Growth of trees at SCBI."}
ggplot() +
  geom_sf(data = growth_scbi, aes(size = growth)) + 
  scale_size(breaks = c(0.01, 0.1, 1), range = c(0.1, 1))
```

@@

```{r}
# Manually define spatial blocks to act as folds
fold1 <- rbind(c(0, 300), c(150, 300), c(150, 600), c(0, 600))
fold2 <- rbind(c(150, 300), c(300, 300), c(300, 600), c(150, 600))

blocks_scbi <- bind_rows(sf_polygon(fold1), sf_polygon(fold2)) %>%
  mutate(folds = c(1, 2) %>% factor())

# Associate each observation to a fold
SpatialBlock_scbi <- spatialBlock(
  speciesData = growth_scbi, k = 2, selection = "systematic", 
  blocks = blocks_scbi, showBlocks = FALSE, verbose = FALSE
)

@@

```{r scbi-spatial-information, out.width="66%", fig.cap="Buffer region and cross-validation block information for SCBI data."}
ggplot() +
  geom_sf_text(data = growth_scbi, aes(label = foldID, col = buffer), alpha = 0.2) +
  geom_sf(data = blocks_scbi, fill = "transparent")
```

@@

```{r, eval = FALSE}
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp")
```
```{r scbi-focal-vs-comp-3, echo = FALSE}
# Not sure why we need to do things this way:
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp") %>% 
  print(n = 5)
```

@@

```{r scbi-posterior-viz, out.width="100%", fig.cap="Posterior distributions of all parameters for a subset of species."}
# Plot posteriors for only a subset of species
sp_to_plot <- c("quru", "litu", "cagl", "cato")

@@

@@

```{r scbi-spatial-cv, eval=TRUE}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  run_cv(comp_dist = comp_dist, cv_grid = blocks_scbi)

focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

>>>>

There are four steps in our modeling pipeline:

1. Compute the growth of trees based on census data.
1. Add spatial information:
    1. Define buffer region trees.
    1. Add spatial cross-validation block information.
1. Identify all focal and corresponding competitor trees.
1. Fit model and make predictions.

Using these four steps, we can address the two following questions of ecological interest:

@@

```{r scbi-trees, out.width="66%", fig.cap="Compute growth of trees based on census data from the Smithsonian Conservation Biology Institute (SCBI)."}
ggplot() +
  geom_sf(data = growth_scbi, aes(size = growth)) + 
  scale_size(breaks = c(0.01, 0.1, 1), range = c(0.1, 1))
```

@@

```{r}
# Manually define spatial blocks to act as folds
fold1 <- rbind(c(0, 300), c(150, 300), c(150, 450), c(0, 450))
fold2 <- rbind(c(150, 300), c(300, 300), c(300, 450), c(150, 450))
fold3 <- rbind(c(0, 450), c(150, 450), c(150, 600), c(0, 600))
fold4 <- rbind(c(150, 450), c(300, 450), c(300, 600), c(150, 600))
n_fold <- 4

blocks_scbi <- bind_rows(
  sf_polygon(fold1), sf_polygon(fold2), sf_polygon(fold3), sf_polygon(fold4)
) %>%
  mutate(folds = c(1:n_fold) %>% factor())

# Associate each observation to a fold
SpatialBlock_scbi <- spatialBlock(
  speciesData = growth_scbi, k = n_fold, selection = "systematic", 
  blocks = blocks_scbi, showBlocks = FALSE, verbose = FALSE
)

@@

```{r scbi-spatial-information, out.width="66%", fig.cap="Add spatial information: Buffer region and spatial cross-validation blocks (1 through 4). All trees in the interior of the study region will be the focal trees whose growth will modeled."}
ggplot() +
  geom_sf_text(data = growth_scbi, aes(label = foldID, col = buffer)) +
  geom_sf(data = blocks_scbi, fill = "transparent")
```

@@

```{r, eval = FALSE}
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp")
```
```{r scbi-focal-vs-comp-3, echo = FALSE}
# Not sure why we need to do things this way:
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp") %>% 
  print(n = 5)
```
```{r scbi-focal-vs-comp-map, out.width="66%", echo = FALSE, fig.cap="Identify all focal and corresponding competitor trees: All 20 competitor trees of focal tree 4."}
comp_radius <- growth_scbi %>% 
  filter(stemID == 4) %>% 
  st_buffer(dist = comp_dist)

comp_radius_box <- growth_scbi %>% 
  filter(stemID == 4) %>% 
  st_buffer(dist = comp_dist + 10) %>% 
  st_bbox() %>% 
  st_as_sfc() %>% 
  st_intersects(growth_scbi, ., sparse = FALSE)

growth_scbi_subset <- growth_scbi %>% 
  mutate(inside = comp_radius_box) %>% 
  filter(inside)

ggplot() +
  geom_sf(data = growth_scbi_subset, aes(col = sp, size = dbh1)) +
  geom_sf(data = comp_radius, linetype = "dashed", alpha = 0, inherit.aes = FALSE) +
  coord_sf(xlim = st_bbox(comp_radius)[c("xmin", "xmax")], ylim = st_bbox(comp_radius)[c("ymin", "ymax")]) +
  geom_sf_text(data = growth_scbi %>% filter(stemID == 4), aes(label = stemID), size = 12) +
  labs(size = "DBH at first census", col = "species")
```

@@

```{r scbi-posterior-viz, out.width="100%", fig.cap="Fit model: Posterior distributions of all parameters for three species."}
# Plot posteriors for only a subset of species
sp_to_plot <- c("litu", "quru", "cagl")

@@

TODO: Discuss meaning of results.

@@

```{r scbi-spatial-cv}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  run_cv(comp_dist = comp_dist, cv_grid = blocks_scbi)
```

```{r}
focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

### 2021-02-19 etc/paper/forestecology.tex
impletemented ideas from Mensh 2017

A high-level overview of the steps of our analysis pipeline is as
follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compute the growth of trees based on census data
\item
  Add spatial information:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    Define buffer region trees.
  \item
    Add spatial cross-validation block information.
  \end{enumerate}
\item
  Identify all focal and corresponding competitor trees.
\item
  Fit model, make predictions, and visualize model results
\end{enumerate}

Additionally,

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth_scbi <-}
\StringTok{  }\KeywordTok{compute_growth}\NormalTok{(}
    \DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi,}
    \DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)),}
    \DataTypeTok{id =} \StringTok{"stemID"}
\NormalTok{  )}
\NormalTok{growth_scbi}
\CommentTok{## Simple feature collection with 7954 features and 8 fields}
\CommentTok{## geometry type:  POINT}
\CommentTok{## dimension:      XY}
\CommentTok{## bbox:           xmin: 0.2 ymin: 300 xmax: 299.9 ymax: 600}
\CommentTok{## CRS:            NA}
\CommentTok{## # A tibble: 7,954 x 9}
\CommentTok{##   stemID sp     dbh1 codes1 status  dbh2 codes2 growth     geometry}
\CommentTok{##    <dbl> <fct> <dbl> <chr>  <chr>  <dbl> <chr>   <dbl>      <POINT>}
\CommentTok{## 1      4 nysy  13.6  M      A       14.2 M       0.103 (14.2 428.5)}
\CommentTok{## 2      5 havi   8.8  M      A        9.6 M;P     0.150  (9.4 436.4)}
\CommentTok{## 3      6 havi   3.25 NULL   A        4   M       0.140    (1.3 434)}
\CommentTok{## 4     77 qual  65.2  M      A       66   M       0.141 (34.7 307.2)}
\CommentTok{## 5     79 tiam  47.7  M      A       46.8 M      -0.161   (40 381.1)}
\CommentTok{## # ... with 7,949 more rows}
\end{Highlighting}
\end{Shaded}

@@

\caption{Growth of trees at SCBI.}\label{fig:scbi-trees}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Manually define spatial blocks to act as folds}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{SpatialBlock_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}
  \DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =} \DecValTok{2}\NormalTok{, }\DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }
  \DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}
\NormalTok{)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf_text}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ foldID, }\DataTypeTok{col =}\NormalTok{ buffer), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ blocks_scbi, }\DataTypeTok{fill =} \StringTok{"transparent"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\caption{Buffer region and cross-validation block information for SCBI data.}\label{fig:scbi-spatial-information}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{cv_grid_sf =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{foldID)}
\CommentTok{## # A tibble: 6,296 x 6}
\CommentTok{##   focal_ID focal_sp   dbh     geometry growth comp             }
\CommentTok{##      <dbl> <fct>    <dbl>      <POINT>  <dbl> <list>           }
\CommentTok{## 1        4 nysy     13.6  (14.2 428.5)  0.103 <tibble [20 x 4]>}
\CommentTok{## 2        5 havi      8.8   (9.4 436.4)  0.150 <tibble [32 x 4]>}
\CommentTok{## 3       79 tiam     47.7    (40 381.1) -0.161 <tibble [20 x 4]>}
\CommentTok{## 4       80 caca      5.15 (38.7 421.7)  0.253 <tibble [12 x 4]>}
\CommentTok{## 5       96 libe      2.3      (60 310)  0.262 <tibble [14 x 4]>}
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi}
\CommentTok{## # A tibble: 6,296 x 8}
\CommentTok{##    focal_ID focal_sp   dbh foldID                  geometry  growth}
\CommentTok{##       <dbl> <fct>    <dbl> <fct>                    <POINT>   <dbl>}
\CommentTok{##  1        4 nysy     13.6  1                   (14.2 428.5)  0.103 }
\CommentTok{##  2        5 havi      8.8  1                    (9.4 436.4)  0.150 }
\CommentTok{##  3       79 tiam     47.7  1                     (40 381.1) -0.161 }
\CommentTok{##  4       80 caca      5.15 1                   (38.7 421.7)  0.253 }
\CommentTok{##  5       96 libe      2.3  1                       (60 310)  0.262 }
\CommentTok{##  6      101 litu     65.4  1                   (47.1 567.3)  0.552 }
\CommentTok{##  7      102 astr      1.99 1                   (40.8 575.5)  0.0954}
\CommentTok{##  8      126 cato     37.4  1                   (60.6 400.2)  0.165 }
\CommentTok{##  9      127 caca      8.72 1                   (72.7 514.1)  0.0370}
\CommentTok{## 10      139 astr      1.71 1                   (96.7 315.1)  0.0549}
\CommentTok{## # ... with 6,286 more rows, and 2 more variables: comp <list>,}
\CommentTok{## #   growth_hat <dbl>}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Plot posteriors for only a subset of species}
\NormalTok{sp_to_plot <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"quru"}\NormalTok{, }\StringTok{"litu"}\NormalTok{, }\StringTok{"cagl"}\NormalTok{, }\StringTok{"cato"}\NormalTok{)}

@@

\caption{Posterior distributions of all parameters for a subset of species.}\label{fig:scbi-posterior-viz}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{cv_grid =}\NormalTok{ blocks_scbi)}

\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{pull}\NormalTok{(.estimate)}
\CommentTok{## [1] 0.1446232}
\end{Highlighting}
\end{Shaded}

>>>>

There are four steps in our modeling pipeline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compute the growth of trees based on census data.
\item
  Add spatial information:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    Define buffer region trees.
  \item
    Add spatial cross-validation block information.
  \end{enumerate}
\item
  Identify all focal and corresponding competitor trees.
\item
  Fit model and make predictions.
\end{enumerate}

Using these four steps, we can address the two following questions of
ecological interest:

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth_scbi <-}
\StringTok{  }\KeywordTok{compute_growth}\NormalTok{(}
    \DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi,}
    \DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)),}
    \DataTypeTok{id =} \StringTok{"stemID"}
\NormalTok{  )}
\NormalTok{growth_scbi}
\CommentTok{## Simple feature collection with 7954 features and 8 fields}
\CommentTok{## geometry type:  POINT}
\CommentTok{## dimension:      XY}
\CommentTok{## bbox:           xmin: 0.2 ymin: 300 xmax: 299.9 ymax: 600}
\CommentTok{## CRS:            NA}
\CommentTok{## # A tibble: 7,954 x 9}
\CommentTok{##    stemID sp     dbh1 codes1 status  dbh2 codes2  growth     geometry}
\CommentTok{##     <dbl> <fct> <dbl> <chr>  <chr>  <dbl> <chr>    <dbl>      <POINT>}
\CommentTok{##  1      4 nysy  13.6  M      A       14.2 M       0.103  (14.2 428.5)}
\CommentTok{##  2      5 havi   8.8  M      A        9.6 M;P     0.150   (9.4 436.4)}
\CommentTok{##  3      6 havi   3.25 NULL   A        4   M       0.140     (1.3 434)}
\CommentTok{##  4     77 qual  65.2  M      A       66   M       0.141  (34.7 307.2)}
\CommentTok{##  5     79 tiam  47.7  M      A       46.8 M      -0.161    (40 381.1)}
\CommentTok{##  6     80 caca   5.15 M      A        6.5 M       0.253  (38.7 421.7)}
\CommentTok{##  7     96 libe   2.3  J;M    A        3.7 M       0.262      (60 310)}
\CommentTok{##  8    100 caca   5.09 NULL   A       NA   DN     NA      (52.5 476.3)}
\CommentTok{##  9    101 litu  65.4  M      A       68.4 M       0.552  (47.1 567.3)}
\CommentTok{## 10    102 astr   1.99 NULL   A        2.5 M       0.0954 (40.8 575.5)}
\CommentTok{## # ... with 7,944 more rows}
\end{Highlighting}
\end{Shaded}

@@

\caption{Compute growth of trees based on census data from the Smithsonian Conservation Biology Institute (SCBI).}\label{fig:scbi-trees}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Manually define spatial blocks to act as folds}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold3 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold4 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{n_fold <-}\StringTok{ }\DecValTok{4}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}
  \KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2), }\KeywordTok{sf_polygon}\NormalTok{(fold3), }\KeywordTok{sf_polygon}\NormalTok{(fold4)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n_fold) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{SpatialBlock_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}
  \DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =}\NormalTok{ n_fold, }\DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }
  \DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}
\NormalTok{)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf_text}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ foldID, }\DataTypeTok{col =}\NormalTok{ buffer)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ blocks_scbi, }\DataTypeTok{fill =} \StringTok{"transparent"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\caption{Add spatial information: Buffer region and spatial cross-validation blocks (1 through 4). All trees in the interior of the study region will be the focal trees whose growth will modeled.}\label{fig:scbi-spatial-information}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{cv_grid_sf =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{foldID)}
\CommentTok{## # A tibble: 6,296 x 6}
\CommentTok{##    focal_ID focal_sp   dbh     geometry  growth comp             }
\CommentTok{##       <dbl> <fct>    <dbl>      <POINT>   <dbl> <list>           }
\CommentTok{##  1        4 nysy     13.6  (14.2 428.5)  0.103  <tibble [20 x 4]>}
\CommentTok{##  2        5 havi      8.8   (9.4 436.4)  0.150  <tibble [32 x 4]>}
\CommentTok{##  3       79 tiam     47.7    (40 381.1) -0.161  <tibble [20 x 4]>}
\CommentTok{##  4       80 caca      5.15 (38.7 421.7)  0.253  <tibble [12 x 4]>}
\CommentTok{##  5       96 libe      2.3      (60 310)  0.262  <tibble [14 x 4]>}
\CommentTok{##  6      101 litu     65.4  (47.1 567.3)  0.552  <tibble [19 x 4]>}
\CommentTok{##  7      102 astr      1.99 (40.8 575.5)  0.0954 <tibble [44 x 4]>}
\CommentTok{##  8      126 cato     37.4  (60.6 400.2)  0.165  <tibble [16 x 4]>}
\CommentTok{##  9      127 caca      8.72 (72.7 514.1)  0.0370 <tibble [14 x 4]>}
\CommentTok{## 10      139 astr      1.71 (96.7 315.1)  0.0549 <tibble [48 x 4]>}
\CommentTok{## # ... with 6,286 more rows}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=0.66\linewidth]{Figures/scbi-focal-vs-comp-map-1}

\caption{Identify all focal and corresponding competitor trees: All 20 competitor trees of focal tree 4.}\label{fig:scbi-focal-vs-comp-map}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi}
\CommentTok{## # A tibble: 6,296 x 8}
\CommentTok{##    focal_ID focal_sp   dbh foldID                  geometry  growth}
\CommentTok{##       <dbl> <fct>    <dbl> <fct>                    <POINT>   <dbl>}
\CommentTok{##  1        4 nysy     13.6  1                   (14.2 428.5)  0.103 }
\CommentTok{##  2        5 havi      8.8  1                    (9.4 436.4)  0.150 }
\CommentTok{##  3       79 tiam     47.7  1                     (40 381.1) -0.161 }
\CommentTok{##  4       80 caca      5.15 1                   (38.7 421.7)  0.253 }
\CommentTok{##  5       96 libe      2.3  1                       (60 310)  0.262 }
\CommentTok{##  6      101 litu     65.4  3                   (47.1 567.3)  0.552 }
\CommentTok{##  7      102 astr      1.99 3                   (40.8 575.5)  0.0954}
\CommentTok{##  8      126 cato     37.4  1                   (60.6 400.2)  0.165 }
\CommentTok{##  9      127 caca      8.72 3                   (72.7 514.1)  0.0370}
\CommentTok{## 10      139 astr      1.71 1                   (96.7 315.1)  0.0549}
\CommentTok{## # ... with 6,286 more rows, and 2 more variables: comp <list>,}
\CommentTok{## #   growth_hat <dbl>}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Plot posteriors for only a subset of species}
\NormalTok{sp_to_plot <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"litu"}\NormalTok{, }\StringTok{"quru"}\NormalTok{, }\StringTok{"cagl"}\NormalTok{)}

@@

\caption{Fit model: Posterior distributions of all parameters for three species.}\label{fig:scbi-posterior-viz}
\end{figure}

TODO: Discuss meaning of results.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{cv_grid =}\NormalTok{ blocks_scbi)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{pull}\NormalTok{(.estimate)}
\CommentTok{## [1] 0.1402209}
\end{Highlighting}
\end{Shaded}
